Parameter estimation

### 2023-05-26 SFE-article/Article_Model_Parameters.tex
08.05
12.05
26.05

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
%Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ is the parameters, and $u$ are control variables, the process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.These sensitivity functions measure the influence of the parameter change on the model's output. As an example, the supercritical extraction process is presented. The impact of mass flow rate, pressure, and inlet temperature on the model's output is discussed. The sensitivity analysis results prove that the considered variables can affect the extraction's yield and be used as control variables in optimization problems. Moreover, the local sensitivity analysis results are analyzed from a phenomenological point of view to enhance understanding of the process model.
%Given a system of partial differential equations, $F(t,x,\dot{x},\Theta,u)=0$, where $x$ represents state variables, $\Theta$ are the parameters, and $u$ are control variables, we describe the supercritical extraction process. The process model describes a partially filled extractor with a fixed bed, which work under constant operating conditions. We assume that the flow is uniform across any cross-section, although the area available for the fluid phase can change along the extractor. We apply the concept of quasi-one-dimensional flow to mimic the modelling of a two-dimensional case.
%In this work, a distributed-parameter model, based on \citet{Reverchon1996} is used to describe a fluid-solid extraction process of caraway oil from caraway seeds with $CO_2$ as a solvent. The model parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient \textit{and saturation concentration} are obtained from parameter estimation. The parameters are estimated based on four experiments performed at $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar and $50^\circ C$/$300$ bar. Given yield data, the model-based parameter estimation uses the maximum likelihood estimation method under assumption of normal error.
A system of partial differential equations, $G(t,x,\dot{x},\Theta,u)=0$ is considered, where $x$ denotes the state variables, $\Theta$ represents the parameters, and $u$ is the control variables. The system $G(t,x,\dot{x},\Theta,u)=0$ describe the supercritical extraction process, which involves a partially filled extractor with a fixed bed that operates under constant conditions. It is assumed that the flow is uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. To model this two-dimensional case, the concept of quasi-one-dimensional flow is applied.
To describe the fluid-solid extraction process of caraway oil from caraway seeds with $CO_2$ as a solvent, we use the distributed-parameter model $G(t,x,\dot{x},\Theta,u)=0$ based on \citet{Reverchon1996}. This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient, saturation concentration, and an initial state estimate. These parameters are estimated from the Peng-Robinson equation of state and by applying the maximum likelihood estimation method on yield data under the normal error assumption.
The dataset comes from four experiments conducted at different operating conditions: $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar, and $50^\circ C$/$300$ bar.

@@

\begin{keywords}
Supercritical extraction \sep Parameter estimation \sep Mathematical modeling
\end{keywords}

@@

{\footnotesize
	\begin{equation*}
		\cfrac{d v}{d \rho_f} = - \cfrac{d v}{dP} \cfrac{d P}{d \rho_f} = -\cfrac{1}{\rho v} \cfrac{dP}{d\rho_f} = -\cfrac{v}{\rho_f}
	\end{equation*}
}

@@

>>>>

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
%Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ is the parameters, and $u$ are control variables, the process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.These sensitivity functions measure the influence of the parameter change on the model's output. As an example, the supercritical extraction process is presented. The impact of mass flow rate, pressure, and inlet temperature on the model's output is discussed. The sensitivity analysis results prove that the considered variables can affect the extraction's yield and be used as control variables in optimization problems. Moreover, the local sensitivity analysis results are analyzed from a phenomenological point of view to enhance understanding of the process model.
%Given a system of partial differential equations, $F(t,x,\dot{x},\Theta,u)=0$, where $x$ represents state variables, $\Theta$ are the parameters, and $u$ are control variables, we describe the supercritical extraction process. The process model describes a partially filled extractor with a fixed bed, which work under constant operating conditions. We assume that the flow is uniform across any cross-section, although the area available for the fluid phase can change along the extractor. We apply the concept of quasi-one-dimensional flow to mimic the modelling of a two-dimensional case.
%In this work, a distributed-parameter model, based on \citet{Reverchon1996} is used to describe a fluid-solid extraction process of caraway oil from caraway seeds with $CO_2$ as a solvent. The model parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient \textit{and saturation concentration} are obtained from parameter estimation. The parameters are estimated based on four experiments performed at $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar and $50^\circ C$/$300$ bar. Given yield data, the model-based parameter estimation uses the maximum likelihood estimation method under assumption of normal error.
The aim of this study was to investigate the supercritical extraction process of the caraway oil from caraway seeds from a partially filled extractor with a fixed bed that was operated under multiple constant operating conditions. The dataset collected from the experiments consists of four experiments conducted at different operating conditions: $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar, and $50^\circ C$/$300$ bar. To describe the fluid-solid extraction process with $CO_2$ as a solvent, a distributed-parameter model is used. It is assumed that the flow is uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. To model this two-dimensional case, the concept of quasi-one-dimensional flow is applied. This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient, saturation concentration, and an initial state estimate. These parameters are estimated from the Peng-Robinson equation of state and by applying the maximum likelihood estimation method on yield data under the normal error assumption.

@@

\begin{keywords}
Supercritical extraction \sep Parameter estimation \sep Mathematical modelling
\end{keywords}

@@

{\footnotesize
	\begin{equation} \label{EQ: Pressure_Velocity}
		\cfrac{d v}{d \rho_f} = - \cfrac{d v}{dP} \cfrac{d P}{d \rho_f} = -\cfrac{1}{\rho v} \cfrac{dP}{d\rho_f} = -\cfrac{v}{\rho_f}
	\end{equation}
}

@@

\clearpage
\subsection{Solution of the parameter estimation starting from another initial guess} \label{CH: Profiles_2}
\subfile{Sections/Parameter_estimation_solution_from_another_IG}

### 2023-05-26 SFE-article/Sections/Thermo_imp.tex
26.05

	\begin{figure*}[H]
		\begin{subfigure}[b]{0.95\textwidth}
			\centering
			\includegraphics[trim = 2.9cm 7cm 3cm 7cm,clip,width=\textwidth]{Figures/Compressibility.pdf}	
			\caption{The compressibility factor based on the Peng-Robinson equation of state}
			\label{fig: SFE_Properties_Compressibility}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.95\textwidth}
			\centering
			\includegraphics[trim = 2.9cm 7cm 3cm 7cm,clip,width=\textwidth]{Figures/RHO.pdf}	
			\caption{The fluid density based on the Peng-Robinson equation of state}
			\label{fig: SFE_Properties_Density}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.95\textwidth}
			\centering
			\includegraphics[trim = 2.9cm 7cm 3.cm 7cm,clip,width=\textwidth]{Figures/CP.pdf}	
			\caption{The specific heat of the $CO_2$ based on the Peng-Robinson equation of state}
			\label{fig: SFE_Properties_CP}
		\end{subfigure}
		\caption{Properties of $CO_2$ based on the equation of state}
		\label{fig: SFE_Properties}
	\end{figure*}

>>>>

	\begin{figure*}[H]
		\begin{subfigure}[b]{0.31\textwidth}
			\centering
			\includegraphics[trim = 2.9cm 8cm 18cm 7cm,clip,width=\textwidth]{Figures/Compressibility.pdf}	
			\caption{The compressibility factor based on the Peng-Robinson equation of state}
			\label{fig: SFE_Properties_Compressibility}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.31\textwidth}
			\centering
			\includegraphics[trim = 2.9cm 8cm 18cm 7cm,clip,width=\textwidth]{Figures/RHO.pdf}	
			\caption{The fluid density based on the Peng-Robinson equation of state}
			\label{fig: SFE_Properties_Density}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.31\textwidth}
			\centering
			\includegraphics[trim = 2.9cm 8cm 18cm 7cm,clip,width=\textwidth]{Figures/CP.pdf}	
			\caption{The specific heat of the $CO_2$ based on the Peng-Robinson equation of state}
			\label{fig: SFE_Properties_CP}
		\end{subfigure}
		\caption{Properties of $CO_2$ based on the equation of state}
		\label{fig: SFE_Properties}
	\end{figure*}
